---
title: "SES Philippines Correlation"
author: "Cole Campton"
date: "7/16/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(haven)
library(DescTools)
library(tidyverse)
library("quantreg")
library(RColorBrewer)

datapath <- "D:/Users/ccampton/Documents/unesco_equity/data/f.PUF_3.Philippines2014-2015-4-Regions_grade1-2_EGRA-SSME_Cebuano-Hiligaynon-Ilokano-Maguindanaoan/4_Final_2014-2015_Student-Level-Data_Philippines_Grade1-2_MotherTongue_EGRA.dta"
data <- read_dta(datapath)

data$treat_phase <- data$year
orf <- "ph_orf"
data$orf <- data[,orf]
features <- c("grade","treat_phase","orf","language")
SESfeat = c()
for(i in 1:9){SESfeat <- c(SESfeat,paste0("exit_interview6",letters[i]))}
SESlabs = c("Electricity","Radio","TV","Car/Motor Cycl","Bike","Kitchen","Computer","Fridge","Phone")

SESmask = rowSums(is.na(data[,SESfeat]))
# data <- na.omit(data[,c("id",features, SESfeat)])


# pie(rep(1,n),col=unlist(colormap))
```

# Missing Data Issue

We note that while the complete dataset contains entries from both 2014 and 2015 in essentially equal parts, entries with non-missing SES data come exclusively from 2014. Furthermore there are no corresponding students measured both in 2014 and 2015 meaning that we may not infer SES information for students in 2015. Going forward this analysis will exclude data missing SES information.

```{r missingdata, echo=TRUE}
table(data$year)
table(data[SESmask,"year"])
length(unique(data$id[data$treat_phase==2014]))+length(unique(data$id[data$treat_phase==2015])) - length(unique(c(data$id[data$treat_phase==2014],data$id[data$treat_phase==2015])))
data <- data[SESmask,]
```
```{r colorsetup, echo=FALSE}
n <- length(unique(data$treat_phase))
qual_col_pals = brewer.pal.info[brewer.pal.info$category == 'qual',]
col_vector = unlist(mapply(brewer.pal,qual_col_pals$maxcolors,rownames(qual_col_pals)))
colormap <- data.frame(matrix(nrow=1,ncol=n))
rownames(colormap) <- "color"
colnames(colormap) <- as.character(unique(data$treat_phase))
colors <- c("#800000","#000075","#3cb44b")
if(n <= length(colors)){
  colormap[as.character(unique(data$treat_phase))] <- colors[1:n]
}else{
  colormap[as.character(unique(data$treat_phase))] <- sample(col_vector,n)
}
```

# Secondary Data Issues

The secondary issue, such that no meaningful analysis may be completed, is that all students with recorded ownership items own exactly the same items. 

```{r dataissues2, echo=FALSE}
ownershipPct <- colSums(na.omit(data[,SESfeat]))/nrow(data)
barplot(ownershipPct,las=2,names.arg=SESlabs,main="Ownership Percent of each Item")
ownershipCts <- colSums(na.omit(data[,SESfeat]))
barplot(ownershipCts,las=2,names.arg=SESlabs,main="Ownership Counts of each Item")
```

<!-- # Coherence and Summary Statistics -->
<!-- First we will describe the percentage of the population which claims ownership of each asset.  -->
<!-- ```{r summary,echo=FALSE} -->
<!-- PCA <- prcomp(na.omit(data[,SESfeat])) -->
<!-- projPC <- function(X) predict(PCA,newdata=X)[,1] -->
<!-- ownershipPct <- colSums(na.omit(data[,SESfeat]))/nrow(data) -->
<!-- barplot(ownershipPct,las=2,names.arg=SESlabs,main="Ownership Percent of each Item") -->
<!-- barplot(PCA$rotation[,1],las=2,names.arg=SESlabs,main="Item weights for First Principle Component") -->
<!-- barplot(PCA$sdev/sum(PCA$sdev),names.arg=1:length(SESfeat),main="Variance explained by each Principle Component") -->
<!-- ``` -->

<!-- <!-- # Quantile Regression differences from Baseline to endline --> -->

<!-- ```{r quantileDiffs,echo=FALSE, warning=FALSE, eval=FALSE, include=FALSE} -->
<!-- subpopFeats = c("grade") -->
<!-- for (i in 1:length(subpopFeats)){ -->
<!--   uniqueFeat = unique(unlist(data[,subpopFeats[i]])) -->
<!--   for (j in 1:length(uniqueFeat)){ -->
<!--     subpopMask <- dataTemporal[,subpopFeats[i]] == uniqueFeat[j]  -->
<!--     SES <- na.omit(dataTemporal[subpopMask,c("orf.base","orf.end",paste0(SESfeat,".base"))]) -->
<!--     colnames(SES) <- c("orf.base","orf.end",SESfeat) -->
<!--     SESindbl <-  projPC(SES[,SESfeat]) -->
<!--     temp <- na.omit(dataTemporal[subpopMask,c("orf.base","orf.end",paste0(SESfeat,".end"))]) -->
<!--     colnames(temp) <- c("orf.base","orf.end",SESfeat) -->
<!--     SESindel <-  projPC(SES[,SESfeat]) -->

<!--     plotrange <- data.frame(X= seq(min(SESind),max(SESind),length=250)) -->

<!--     Ybl = unlist(SES[,"orf.base"]) -->
<!--     Xbl = SESindbl -->

<!--     regdatabl <- data.frame(X= Xbl,Y=Ybl) -->
<!--     quadratbl <- Y~ a*X^2+b*X+c -->
<!--     fit15.rqbl <- nlrq(quadratbl, data=regdatabl, start= list(a=1,b=1,c=1),tau=.15) -->
<!--     fit85.rqbl <- nlrq(quadratbl, data=regdatabl, start= list(a=1,b=1,c=1),tau=.85) -->
<!--     reg15bl <- within(plotrange,Y <- predict(fit15.rqbl, newdata= plotrange)) -->
<!--     reg85bl <- within(plotrange,Y <- predict(fit85.rqbl, newdata= plotrange)) -->

<!--     Yel = unlist(SES[,"orf.end"]) -->
<!--     Xel = SESindel -->

<!--     regdatael <- data.frame(X= Xel,Y=Yel) -->
<!--     quadratel <- Y~ a*X^2+b*X+c -->
<!--     fit15.rqel <- nlrq(quadratel, data=regdatael, start= list(a=1,b=1,c=1),tau=.15) -->
<!--     fit85.rqel <- nlrq(quadratel, data=regdatael, start= list(a=1,b=1,c=1),tau=.85) -->
<!--     reg15el <- within(plotrange,Y <- predict(fit15.rqel, newdata= plotrange)) -->
<!--     reg85el <- within(plotrange,Y <- predict(fit85.rqel, newdata= plotrange)) -->

<!--     difference15 <- data.frame(X=reg15el$X ,Y=(reg15el$Y- reg15bl$Y)) -->
<!--     difference85 <- data.frame(X=reg85el$X ,Y=(reg85el$Y- reg85bl$Y)) -->
<!--     plot((Xbl+Xel)/2,Yel-Ybl,main=paste0("Difference of Quantile Regressions, grade",uniqueFeat[j] )) -->
<!--     lines(Y~X, data =difference15,add=TRUE, col ="red") -->
<!--     lines(Y~X, data =difference85, add=TRUE,col = "blue") -->


<!--   } -->
<!-- } -->
<!-- ``` -->


<!-- # N-tile SES-index Analysis of Gini and Mean ORF -->
<!-- First we conduct quantile analysis, evaluating the Gini coefficient, mean ORF, CV, and percent zero for each of the 2,3,4-tiles of our SES index.  -->
<!-- We segment into subpopulations by language and grade, producing quantile regressions for  -->
<!-- It appears from the above analysis that the majority of change in MRF occurs in the lowest tertile of wealth.  -->

<!-- ```{r ntiles,echo=FALSE, warning=FALSE} -->
<!-- ntiles = c(2,3,4) -->
<!-- normorf <- matrix(NA, ncol=1,nrow=nrow(data)) -->

<!-- phases <- sort(unlist(unique(unlist(data[,"treat_phase"])))) -->
<!-- nphases <- length(phases) -->
<!-- SESind <-  projPC(data) -->
<!-- subpopVars <- c("language","grade") -->
<!-- #Compute Subpop labels, and masks for non-empty subpops (uses all phases) -->
<!-- { -->
<!--   subpopVars <- subpopVars[unlist(lapply(subpopVars, function(x) length(unlist(unique(data[,x])))))>1] -->
<!--   subpops <- "" -->
<!--   for(i in 1:length(subpopVars)){subpops <- unique(paste0(subpops,unique(unlist(data[,subpopVars[i]]))))} -->
<!--   nsubpops <- length(subpops) -->
<!--   subpoplabels <- "" -->
<!--   for(i in 1:length(subpopVars)){subpoplabels <- unique(paste0(subpoplabels,subpopVars[i]," ",sort(unique(unlist(data[,subpopVars[i]])))," "))} -->
<!--   subpopmasks <- matrix(ncol=nsubpops,nrow=length(SESind)) -->
<!--   for(sp in 1:nsubpops){ -->
<!--     masktemp <- rep(TRUE, length(SESind)) -->
<!--     for(spv in 1:length(subpopVars)){ -->
<!--       masktemp <- masktemp & (as.character(unlist(data[,subpopVars[spv]]))==substr(subpops[sp],spv,spv)) -->
<!--     } -->
<!--     subpopmasks[,sp] <- masktemp -->
<!--   } -->
<!--   nonemptysubpop <- colSums(subpopmasks)>0 -->
<!--   subpoplabels <- subpoplabels[nonemptysubpop] -->
<!--   subpops <- subpops[nonemptysubpop] -->
<!--   subpopmasks <- subpopmasks[,nonemptysubpop] -->
<!--   nsubpops <- length(subpops) -->
<!-- } -->

<!-- for(ns in 1:length(ntiles)){ -->
<!-- ntile = ntiles[ns] -->
<!-- # Generate n-tile masks -->
<!-- { -->
<!--   ntilemasks <- matrix(ncol=ntile,nrow=length(SESind)) -->
<!--   for(p in 1:(ntile)){ -->
<!--     ntilemasks[,p] <- (SESind<quantile(SESind, (p)/(ntile))) & (SESind>=quantile(SESind, (p-1)/ntile)) -->
<!--   } -->
<!-- } -->
<!-- # Intialize table, build labels -->
<!-- { -->
<!--   ntileTab <- data.frame(matrix(ncol=(nphases*nsubpops+2),nrow=(4*(ntile+1)+2))) -->
<!--   ntileTab[(0:3)*(ntile+1)+3,1] <- c("Gini","CV","%0","MRF") -->
<!--   ntileTab[3:(4*(ntile+1)+2),2] <- rep(c(1:ntile,"All"), 4) -->
<!--   ntileTab[1,(1:nsubpops)*nphases+1] <- c(subpoplabels) -->
<!--   ntileTab[2,0:(nphases*nsubpops)+2] <- c("Q#",rep(phases,nsubpops)) -->
<!-- } -->
<!-- for(sp in 1:nsubpops){ -->
<!--   SES <- na.omit(data[subpopmasks[,sp],c("orf","treat_phase",SESfeat)]) -->
<!--   #ORF verse SES index by sub-populations -->
<!--   if(ns==1){ -->
<!--     SESind <-  projPC(SES[,SESfeat]) -->
<!--     plcolors <- alpha(unlist(lapply(SES$treat_phase,function(x) colormap[as.character(x)])),.4) -->
<!--     plot(SESind,unlist(SES$orf),col=plcolors, main= paste0("ORF verse SES index by phase, ",subpoplabels[sp] )) -->
<!--     legend("topleft", legend=colnames(colormap), pch=16,col=unlist(colormap)) -->
<!--   } -->
<!--   for( p in 1:nphases){ -->
<!--     phase = phases[p] -->
<!--     phasemask <- as.character(SES$treat_phase)==as.character(phase) -->
<!--     # #ORF verse SES index colored by treatment phase -->
<!--     if(ns==1){ -->
<!--       if(sum(phasemask)>0){ -->
<!--         Y = unlist(SES[phasemask,"orf"]) -->
<!--         X = SESind[phasemask] -->
<!--         regdata <- data.frame(X= X,Y=Y) -->
<!--         quadrat <- Y~ a*X^2+b*X+c -->
<!--         fit15.rq <- nlrq(quadrat, data=regdata, start= list(a=1,b=1,c=1),tau=.15) -->
<!--         fit85.rq <- nlrq(quadrat, data=regdata, start= list(a=1,b=1,c=1),tau=.85) -->
<!--         plotrange <- data.frame(X= seq(min(SESind),max(SESind),length=250)) -->
<!--         reg15 <- within(plotrange,Y <- predict(fit15.rq, newdata= plotrange)) -->
<!--         lines(Y~X, data =reg15, col= unlist(colormap[as.character(phase)]), add=TRUE) -->
<!--         reg85 <- within(plotrange,Y <- predict(fit85.rq, newdata= plotrange)) -->
<!--         lines(Y~X, data =reg85, col= unlist(colormap[as.character(phase)]), add=TRUE) -->
<!--         print(paste0("Treat phase ",phase," quantile regression tests:")) -->
<!--         print(summary(fit15.rq)) -->
<!--         print(summary(fit85.rq)) -->
<!--       } -->
<!--     } -->
<!--     #Compute normalize orf for phase, subpop -->
<!--     if(ns==1){ -->
<!--         normMask <- subpopmasks[,sp] & unlist(as.character(data$treat_phase)==as.character(phase)) -->
<!--         if(sum(normMask)>0){ -->
<!--         spMean <- mean(unlist(SES[phasemask,"orf"])) -->
<!--         spVar <- var(unlist(SES[phasemask,"orf"])) -->
<!--         normorf[normMask] <- (unlist(data[normMask,"orf"]) - spMean)/spVar -->
<!--         } -->
<!--     } -->
<!--     #Overall phase, subpop measures -->
<!--     { -->
<!--     SESphase <- unlist(na.omit(SES[phasemask,"orf"])) -->
<!--     if(sum(phasemask)>0){ -->
<!--     ntileTab[2+(ntile+1),2+nphases*(sp-1)+p] <- Gini(SESphase) #gini Qi -->

<!--     ntileTab[2+2*(ntile+1),2+nphases*(sp-1)+p] <- sd(SESphase)/mean(SESphase) #CV Qi -->

<!--     ntileTab[2+3*(ntile+1),2+nphases*(sp-1)+p] <- sum(SESphase==0)/length(SESphase)#%0 Qi -->

<!--     ntileTab[2+4*(ntile+1),2+nphases*(sp-1)+p] <- mean(SESphase) #MRF Qi -->
<!--     } -->
<!--     } -->
<!--     # Add n-tile measures for of of the n n-tiles -->
<!--     for(i in 1:ntile){ -->
<!--       phase = phases[p] -->
<!--       ntileSubpopMask <- ntilemasks[,i] & subpopmasks[,sp] & as.character(data$treat_phase)==as.character(phase) -->
<!--       if(sum(ntileSubpopMask)>0){ -->
<!--       SESntile <- unlist(na.omit(data[ntileSubpopMask,"orf"])) -->

<!--       ntileTab[2+i,2+nphases*(sp-1)+p] <- Gini(SESntile) #gini Qi -->

<!--       ntileTab[2+1*(ntile+1)+i,2+nphases*(sp-1)+p] <- sd(SESntile)/mean(SESntile) #CV Qi -->

<!--       ntileTab[2+2*(ntile+1)+i,2+nphases*(sp-1)+p] <- sum(SESntile==0)/length(SESntile)#%0 Qi -->

<!--       ntileTab[2+3*(ntile+1)+i,2+nphases*(sp-1)+p] <- mean(SESntile) #MRF Qi -->
<!--       ntileTab[3:nrow(ntileTab),2+nphases*(sp-1)+p] <- round(as.numeric(ntileTab[3:nrow(ntileTab),2+nphases*(sp-1)+p]),digits=3) -->
<!--       } -->
<!--       } -->
<!--   } -->
<!--   #T-test for ??? -->
<!--   {   -->
<!-- # LowestNtileMRFchange <- data[ntilemasks[,1] & subpopmasks[,sp] & data$treat_phase==phases[1],"orf"]-data[ntilemasks[,1] & subpopmasks[,sp] & data$treat_phase==phases[length(phases)],"orf"] -->
<!-- # TopNtileMRFchange <- dataTemporal[ntilemasks[,ncol(ntilemasks)] & subpopmasks[,sp],"orf.end"]-dataTemporal[ntilemasks[,ncol(ntilemasks)] & subpopmasks[,sp],"orf.base"] -->
<!-- # print(t.test(LowestNtileMRFchange,TopNtileMRFchange)) -->
<!--   } -->
<!-- } -->

<!-- # Subpop-normalized plots -->
<!-- if(ns==1){ -->
<!-- SES <- na.omit(data[,c("treat_phase",SESfeat)]) -->
<!-- SESind <-  projPC(SES[,SESfeat]) -->
<!-- plot(SESind,normorf,col=plcolors, main= "Population-normalized ORF verse SES index") -->
<!-- legend("topleft", legend=colnames(colormap), pch=16,col=unlist(colormap)) -->
<!-- for( k in unique(as.factor(SES$treat_phase))){ -->
<!--     Y = normorf[as.character(SES$treat_phase)==k] -->
<!--     X = SESind[as.character(SES$treat_phase)==k] -->
<!--     regdata <- data.frame(X= X,Y=Y) -->
<!--     quadrat <- Y~ a*X^2+b*X+c -->
<!--     fit15.rq <- nlrq(quadrat, data=regdata, start= list(a=1,b=1,c=1),tau=.15) -->
<!--     fit85.rq <- nlrq(quadrat, data=regdata, start= list(a=1,b=1,c=1),tau=.85) -->
<!--     plotrange <- data.frame(X= seq(min(SESind),max(SESind),length=250)) -->
<!--     reg15 <- within(plotrange,Y <- predict(fit15.rq, newdata= plotrange)) -->
<!--     lines(Y~X, data =reg15, col= unlist(colormap[as.character(k)]), add=TRUE) -->
<!--     reg85 <- within(plotrange,Y <- predict(fit85.rq, newdata= plotrange)) -->
<!--     lines(Y~X, data =reg85, col= unlist(colormap[as.character(k)]), add=TRUE) -->
<!--     print(paste0("Treat phase ",k," quantile regression tests:")) -->
<!--     print(summary(fit15.rq)) -->
<!--     print(summary(fit85.rq)) -->
<!--   } -->
<!-- } -->

<!-- ntileTab[is.na(ntileTab)] <- "" -->
<!-- print(ntileTab, row.names=FALSE,col.names=FALSE) -->

<!-- } -->

<!-- ``` -->

<!-- # Linear Model Tables and Plots -->
<!-- ```{r ntilesLM,echo=FALSE, warning=FALSE} -->
<!-- ntiles = c(2,3,4) -->
<!-- normorf <- matrix(NA, ncol=1,nrow=nrow(data)) -->

<!-- phases <- sort(unlist(unique(unlist(data[,"treat_phase"])))) -->
<!-- nphases <- length(phases) -->

<!-- temp <- unlist(data$orf) -->
<!-- for(i in 1:length(SESfeat)){temp <- cbind(temp,unlist(data[,SESfeat[i]]))} -->
<!-- rownames(temp) <- 1:nrow(temp) -->
<!-- colnames(temp) <- c("orf",SESfeat) -->
<!-- temp <- data.frame(temp) -->
<!-- lmmodel <- lm(orf~.-orf,data=temp) -->
<!-- SESind <- predict(lmmodel, newdata = temp) -->

<!-- subpopVars <- c("language","grade") -->
<!-- #Compute Subpop labels, and masks for non-empty subpops (uses all phases) -->
<!-- { -->
<!--   subpopVars <- subpopVars[unlist(lapply(subpopVars, function(x) length(unlist(unique(data[,x])))))>1] -->
<!--   subpops <- "" -->
<!--   for(i in 1:length(subpopVars)){subpops <- unique(paste0(subpops,unique(unlist(data[,subpopVars[i]]))))} -->
<!--   nsubpops <- length(subpops) -->
<!--   subpoplabels <- "" -->
<!--   for(i in 1:length(subpopVars)){subpoplabels <- unique(paste0(subpoplabels,subpopVars[i]," ",sort(unique(unlist(data[,subpopVars[i]])))," "))} -->
<!--   subpopmasks <- matrix(ncol=nsubpops,nrow=length(SESind)) -->
<!--   for(sp in 1:nsubpops){ -->
<!--     masktemp <- rep(TRUE, length(SESind)) -->
<!--     for(spv in 1:length(subpopVars)){ -->
<!--       masktemp <- masktemp & (as.character(unlist(data[,subpopVars[spv]]))==substr(subpops[sp],spv,spv)) -->
<!--     } -->
<!--     subpopmasks[,sp] <- masktemp -->
<!--   } -->
<!--   nonemptysubpop <- colSums(subpopmasks)>0 -->
<!--   subpoplabels <- subpoplabels[nonemptysubpop] -->
<!--   subpops <- subpops[nonemptysubpop] -->
<!--   subpopmasks <- subpopmasks[,nonemptysubpop] -->
<!--   nsubpops <- length(subpops) -->
<!-- } -->

<!-- for(ns in 1:length(ntiles)){ -->
<!-- ntile = ntiles[ns] -->
<!-- # Generate n-tile masks -->
<!-- { -->
<!--   ntilemasks <- matrix(ncol=ntile,nrow=length(SESind)) -->
<!--   for(p in 1:(ntile)){ -->
<!--     ntilemasks[,p] <- (SESind<quantile(SESind, (p)/(ntile))) & (SESind>=quantile(SESind, (p-1)/ntile)) -->
<!--   } -->
<!-- } -->
<!-- # Intialize table, build labels -->
<!-- { -->
<!--   ntileTab <- data.frame(matrix(ncol=(nphases*nsubpops+2),nrow=(4*(ntile+1)+2))) -->
<!--   ntileTab[(0:3)*(ntile+1)+3,1] <- c("Gini","CV","%0","MRF") -->
<!--   ntileTab[3:(4*(ntile+1)+2),2] <- rep(c(1:ntile,"All"), 4) -->
<!--   ntileTab[1,(1:nsubpops)*nphases+1] <- c(subpoplabels) -->
<!--   ntileTab[2,0:(nphases*nsubpops)+2] <- c("Q#",rep(phases,nsubpops)) -->
<!-- } -->
<!-- for(sp in 1:nsubpops){ -->
<!--   SES <- na.omit(data[subpopmasks[,sp],c("orf","treat_phase",SESfeat)]) -->
<!--   #ORF verse SES index by sub-populations -->
<!--   if(ns==1){ -->
<!--     SESindsub <-  SESind[subpopmasks[,sp]] -->
<!--     plcolors <- alpha(unlist(lapply(SES$treat_phase,function(x) colormap[as.character(x)])),.4) -->
<!--     plot(SESindsub,unlist(SES$orf),col=plcolors, main= paste0("ORF verse SES index by phase, ",subpoplabels[sp] )) -->
<!--     legend("topleft", legend=colnames(colormap), pch=16,col=unlist(colormap)) -->
<!--   } -->
<!--   for( p in 1:nphases){ -->
<!--     phase = phases[p] -->
<!--     phasemask <- as.character(SES$treat_phase)==as.character(phase) -->
<!--     # #ORF verse SES index colored by treatment phase -->
<!--     if(ns==1){ -->
<!--       if(sum(phasemask)>0){ -->
<!--         Y = unlist(SES[phasemask,"orf"]) -->
<!--         X = SESindsub[phasemask] -->
<!--         regdata <- data.frame(X= X,Y=Y) -->
<!--         quadrat <- Y~ a*X^2+b*X+c -->
<!--         fit15.rq <- nlrq(quadrat, data=regdata, start= list(a=1,b=1,c=1),tau=.15) -->
<!--         fit85.rq <- nlrq(quadrat, data=regdata, start= list(a=1,b=1,c=1),tau=.85) -->
<!--         plotrange <- data.frame(X= seq(min(SESind),max(SESind),length=250)) -->
<!--         reg15 <- within(plotrange,Y <- predict(fit15.rq, newdata= plotrange)) -->
<!--         lines(Y~X, data =reg15, col= unlist(colormap[as.character(phase)]), add=TRUE) -->
<!--         reg85 <- within(plotrange,Y <- predict(fit85.rq, newdata= plotrange)) -->
<!--         lines(Y~X, data =reg85, col= unlist(colormap[as.character(phase)]), add=TRUE) -->
<!--         print(paste0("Treat phase ",phase," quantile regression tests:")) -->
<!--         print(summary(fit15.rq)) -->
<!--         print(summary(fit85.rq)) -->
<!--       } -->
<!--     } -->
<!--     #Compute normalize orf for phase, subpop -->
<!--     if(ns==1){ -->
<!--         normMask <- subpopmasks[,sp] & unlist(as.character(data$treat_phase)==as.character(phase)) -->
<!--         if(sum(normMask)>0){ -->
<!--         spMean <- mean(unlist(SES[phasemask,"orf"])) -->
<!--         spVar <- var(unlist(SES[phasemask,"orf"])) -->
<!--         normorf[normMask] <- (unlist(data[normMask,"orf"]) - spMean)/spVar -->
<!--         } -->
<!--     } -->
<!--     #Overall phase, subpop measures -->
<!--     { -->
<!--     SESphase <- unlist(na.omit(SES[phasemask,"orf"])) -->
<!--     if(sum(phasemask)>0){ -->
<!--     ntileTab[2+(ntile+1),2+nphases*(sp-1)+p] <- Gini(SESphase) #gini Qi -->

<!--     ntileTab[2+2*(ntile+1),2+nphases*(sp-1)+p] <- sd(SESphase)/mean(SESphase) #CV Qi -->

<!--     ntileTab[2+3*(ntile+1),2+nphases*(sp-1)+p] <- sum(SESphase==0)/length(SESphase)#%0 Qi -->

<!--     ntileTab[2+4*(ntile+1),2+nphases*(sp-1)+p] <- mean(SESphase) #MRF Qi -->
<!--     } -->
<!--     } -->
<!--     # Add n-tile measures for of of the n n-tiles -->
<!--     for(i in 1:ntile){ -->
<!--       phase = phases[p] -->
<!--       ntileSubpopMask <- ntilemasks[,i] & subpopmasks[,sp] & as.character(data$treat_phase)==as.character(phase) -->
<!--       if(sum(ntileSubpopMask)>0){ -->
<!--       SESntile <- unlist(na.omit(data[ntileSubpopMask,"orf"])) -->

<!--       ntileTab[2+i,2+nphases*(sp-1)+p] <- Gini(SESntile) #gini Qi -->

<!--       ntileTab[2+1*(ntile+1)+i,2+nphases*(sp-1)+p] <- sd(SESntile)/mean(SESntile) #CV Qi -->

<!--       ntileTab[2+2*(ntile+1)+i,2+nphases*(sp-1)+p] <- sum(SESntile==0)/length(SESntile)#%0 Qi -->

<!--       ntileTab[2+3*(ntile+1)+i,2+nphases*(sp-1)+p] <- mean(SESntile) #MRF Qi -->
<!--       ntileTab[3:nrow(ntileTab),2+nphases*(sp-1)+p] <- round(as.numeric(ntileTab[3:nrow(ntileTab),2+nphases*(sp-1)+p]),digits=3) -->
<!--       } -->
<!--       } -->
<!--   } -->
<!-- } -->

<!-- # Subpop-normalized plots -->
<!-- if(ns==1){ -->
<!-- SES <- na.omit(data[,c("treat_phase",SESfeat)]) -->
<!-- plot(SESind,normorf,col=plcolors, main= "Population-normalized ORF verse SES index") -->
<!-- legend("topleft", legend=colnames(colormap), pch=16,col=unlist(colormap)) -->
<!-- for( k in unique(as.factor(SES$treat_phase))){ -->
<!--     Y = normorf[as.character(SES$treat_phase)==k] -->
<!--     X = SESind[as.character(SES$treat_phase)==k] -->
<!--     regdata <- data.frame(X= X,Y=Y) -->
<!--     quadrat <- Y~ a*X^2+b*X+c -->
<!--     fit15.rq <- nlrq(quadrat, data=regdata, start= list(a=1,b=1,c=1),tau=.15) -->
<!--     fit85.rq <- nlrq(quadrat, data=regdata, start= list(a=1,b=1,c=1),tau=.85) -->
<!--     plotrange <- data.frame(X= seq(min(SESind),max(SESind),length=250)) -->
<!--     reg15 <- within(plotrange,Y <- predict(fit15.rq, newdata= plotrange)) -->
<!--     lines(Y~X, data =reg15, col= unlist(colormap[as.character(k)]), add=TRUE) -->
<!--     reg85 <- within(plotrange,Y <- predict(fit85.rq, newdata= plotrange)) -->
<!--     lines(Y~X, data =reg85, col= unlist(colormap[as.character(k)]), add=TRUE) -->
<!--     print(paste0("Treat phase ",k," quantile regression tests:")) -->
<!--     print(summary(fit15.rq)) -->
<!--     print(summary(fit85.rq)) -->
<!--   } -->
<!-- } -->

<!-- ntileTab[is.na(ntileTab)] <- "" -->
<!-- print(ntileTab, row.names=FALSE,col.names=FALSE) -->

<!-- } -->

<!-- ``` -->
