---
title: "SES PRIMR Correlation"
author: "Cole Campton"
date: "7/16/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(haven)
library(DescTools)
library(tidyverse)
library("quantreg")
library(RColorBrewer)
library(caret)
library(e1071)

datapath <- "D:/Users/ccampton/Documents/unesco_equity/data/PUF_3.Kenya PRIMR2012-2013-Endline_grade1 2_EGRA EGMA ENG HT T TAC COR COM CIN_Eng Kis.dta"
data <- read_dta(datapath)

features <- c("grade","treat_phase","orf")
SESfeat = c()
for(i in 2:10){SESfeat <- c(SESfeat,paste0("exit_interview",i))}
SESlabs = c("Radio","Telephone","Electricity","TV","Fridge","Toilet inside","Bike","Car/Motor Cycl","Motor Veh")

Dbase <- data.frame(data[data$treat_phase==1,c("id",features,SESfeat)])
Dmid <- data.frame(data[data$treat_phase==2,c("id",features,SESfeat)])
Dend <- data.frame(data[data$treat_phase==6,c("id",features,SESfeat)])
# There are no paired ids for baseline to midline of baseline to endline. 
dataTemporal <- merge(Dmid,Dend, by= c("id","grade"),suffixes = c(".base",".end"))
dataTemporal <- na.omit(dataTemporal)

n <- length(unique(data$treat_phase))
qual_col_pals = brewer.pal.info[brewer.pal.info$category == 'qual',]

col_vector = unlist(mapply(brewer.pal,qual_col_pals$maxcolors,rownames(qual_col_pals)))
colormap <- data.frame(matrix(nrow=1,ncol=n))
rownames(colormap) <- "color"
colnames(colormap) <- as.character(unique(data$treat_phase))
# colormap[as.character(unique(data$treat_phase))]= sample(col_vector,n)
colormap[as.character(unique(data$treat_phase))]= c("#800000","#000075","#3cb44b")
pie(rep(1,n),col=unlist(colormap))
```

# Coherence and Summary Statistics

First we will describe the percentage of the population which claims ownership of each asset. 
```{r summary,echo=FALSE}
PCA <- prcomp(na.omit(data[,SESfeat]))
projPC <- function(X) predict(PCA,newdata=X)[,1]
ownershipPct <- colSums(dataTemporal[,paste0(SESfeat,".base")])/nrow(dataTemporal)
barplot(ownershipPct,las=2,names.arg=SESlabs,main="Ownership Percent of each Item")
barplot(PCA$rotation[,1],las=2,names.arg=SESlabs,main="Item weights for First Principle Component")
barplot(PCA$sdev/sum(PCA$sdev),names.arg=1:length(SESfeat),main="Variance explained by each Principle Component")
```
Second we are interested in the time-related coherence of the data. That is, we are curious how many of the students answered ownership questions consistently from baseline to endline. On average each student changed their response to 2.44 of the 9 questions from baseline to endline. Approximately 93% of students changed at least one ownership question answer from baseline to endline, with 63% of these claiming that they no longer had possessions that they claimed to previously own.
```{r coherence}
sum(dataTemporal[paste0(SESfeat,".base")]!=dataTemporal[paste0(SESfeat,".end")])/nrow(dataTemporal)
sum(rowSums(dataTemporal[paste0(SESfeat,".base")]!=dataTemporal[paste0(SESfeat,".end")])>0)/nrow(dataTemporal)*100
sum(rowSums(dataTemporal[paste0(SESfeat,".base")]>dataTemporal[paste0(SESfeat,".end")])>0)/nrow(dataTemporal)*100
```
The above fact is a good indicator of the difficulty inherent in inferring based on this SES data. 

```{r quantileMisclass, echo=FALSE}
temp <- dataTemporal[,paste0(SESfeat,".base")]
colnames(temp) <- SESfeat
BLitemsowned <- rowSums(temp)
SESBL <-  projPC(temp)
temp <- dataTemporal[,paste0(SESfeat,".end")]
ELitemsowned <- rowSums(temp)
colnames(temp) <- SESfeat
SESEL <-  projPC(temp)
quartBL <- rep(NA,length(SESBL))
quartEL <- rep(NA,length(SESEL))
ntile = 4 
for(p in 1:(ntile)){
  quartBL[(SESBL<quantile(SESBL, (p)/(ntile))) & (SESBL>=quantile(SESBL, (p-1)/ntile))] <- p
  quartEL[(SESBL<quantile(SESEL, (p)/(ntile))) & (SESEL>=quantile(SESEL, (p-1)/ntile))] <- p
}
plot(SESBL,SESEL, main="SES index at Endline vs Baseline")
confmat <- confusionMatrix(as.factor(quartBL), as.factor(quartEL), dnn=c("Basline","Endline"))$table
cat("Confusion matrix of quartiles based on Baseline/Endline SES Questions. \n")
print(confmat)
plot(SESBL,BLitemsowned,ylab="#items owned",main="Items owned BL vs SES Index")
plot(SESEL,ELitemsowned,ylab="#items owned",main="Items owned EL vs SES Index")
```
# Stratified by Grade

The first model we investigate stratifies the dataset by grade, acknowledging that within each age group Oral Reading Fluency (ORF) may be differently correlated with social economic status. For each grade level we extract the first principle component of the normalize (i.e. 0 mean, variance 1 transformed) asset ownership binary variables. This first principle component is used as a linear weighting scheme to produce a SES index. We plot the ORFof students verse this SSE index, colored by treatment phase. Additionally we attempt to model ORF with a logistic regression of asset ownership variables and measure the correlation of our indices with ORF within each treatment phase and grade pairing. 

```{r noTreatPhase,echo=FALSE, warning=FALSE}
subpopFeats = c("grade")
for (i in 1:length(subpopFeats)){
  uniqueFeat = unique(unlist(data[,subpopFeats[i]]))
  for (j in 1:length(uniqueFeat)){
    subpopMask <- data[,subpopFeats[i]] == uniqueFeat[j] 
    SES <- na.omit(data[subpopMask,c(features,SESfeat)])
    SESind <-  projPC(SES[,SESfeat])
    plcolors <- alpha(unlist(lapply(SES$treat_phase,function(x) colormap[as.character(x)])),.4)
    plot(SESind,SES$orf,col=plcolors, main= paste0("ORF verse SES index colored by treatment phase, grade ",uniqueFeat[j] ))
    legend("topleft", legend=colnames(colormap), pch=16,col=unlist(colormap))
    # plot(SESind,SES$orf,col=as.factor(SES$treat_phase), main= paste0("ORF verse SES index colored by treatment phase for grade ",uniqueFeat[j] ))
    # legend("topleft", legend=levels(as.factor(SES$treat_phase)), pch=16,col=unique(as.factor(SES$treat_phase)))
    # abline(1,0)
    for( k in unique(as.factor(SES$treat_phase))){
    Y = unlist(SES[as.character(SES$treat_phase)==k,"orf"])
    X = SESind[as.character(SES$treat_phase)==k]
    # plot(X, Y,main = paste0("ORF verse SES index for grade ",uniqueFeat[j]," treat phase ",k),col='red')
    regdata <- data.frame(X= X,Y=Y)
    quadrat <- Y~ a*X^2+b*X+c
    fit15.rq <- nlrq(quadrat, data=regdata, start= list(a=1,b=1,c=1),tau=.15)
    fit85.rq <- nlrq(quadrat, data=regdata, start= list(a=1,b=1,c=1),tau=.85)
    plotrange <- data.frame(X= seq(min(SESind),max(SESind),length=250))
    reg15 <- within(plotrange,Y <- predict(fit15.rq, newdata= plotrange))
    lines(Y~X, data =reg15, col= unlist(colormap[as.character(k)]), add=TRUE)
    reg85 <- within(plotrange,Y <- predict(fit85.rq, newdata= plotrange))
    lines(Y~X, data =reg85, col= unlist(colormap[as.character(k)]), add=TRUE)
    print(paste0("Treat phase ",k," quantile regression tests:"))
    print(summary(fit15.rq))
    print(summary(fit85.rq))
    # fit15.rq <- rq(Y~X,tau=.15)
    # fit85.rq <- rq(Y~X,tau=.85)
    # abline(fit15.rq$coefficients[1],fit15.rq$coefficients[2],col=as.factor(as.numeric(k)))
    # abline(fit85.rq$coefficients[1],fit85.rq$coefficients[2],col=as.factor(as.numeric(k)))
    # abline(fit15.rq$coefficients[1],fit15.rq$coefficients[2],col=unlist(colormap[as.character(k)]))
    # abline(fit85.rq$coefficients[1],fit85.rq$coefficients[2],col=unlist(colormap[as.character(k)]))
    }
    
    stratmodel <- lm(orf~.-grade-orf-treat_phase,data=SES)
    SESlm <- predict(stratmodel, newdata = SES)
    
    plot(SESlm,SES$orf,col=plcolors, main= paste0("ORF verse SES linear model colored by treatment phase, grade ",uniqueFeat[j] ))
    legend("topleft", legend=colnames(colormap), pch=16,col=unlist(colormap))
    # plot(SESlm, SES$orf,col=as.factor(SES$treat_phase),main= paste0("ORF verse SES linear model colored by treatment phase for grade ",uniqueFeat[j] ))
    # legend("topleft", legend=levels(as.factor(SES$treat_phase)), pch=16,col=unique(as.factor(SES$treat_phase)))
    # abline(1,0)
   for( k in unique(as.factor(SES$treat_phase))){
    Y = unlist(SES[as.character(SES$treat_phase)==k,"orf"])
    X = SESlm[as.character(SES$treat_phase)==k]
    regdata <- data.frame(X= X,Y=Y)
    quadrat <- Y~ a*X^2+b*X+c
    fit15.rq <- nlrq(quadrat, data=regdata, start= list(a=1,b=1,c=1),tau=.15)
    fit85.rq <- nlrq(quadrat, data=regdata, start= list(a=1,b=1,c=1),tau=.85)
    plotrange <- data.frame(X= seq(min(SESlm),max(SESlm),length=250))
    reg15 <- within(plotrange,Y <- predict(fit15.rq, newdata= plotrange))
    lines(Y~X, data =reg15, col= unlist(colormap[as.character(k)]), add=TRUE)
    reg85 <- within(plotrange,Y <- predict(fit85.rq, newdata= plotrange))
    lines(Y~X, data =reg85, col= unlist(colormap[as.character(k)]), add=TRUE)
    print(paste0("Treat phase ",k," quantile regression tests:"))
    print(summary(fit15.rq))
    print(summary(fit85.rq))
    # plot(X, Y,main = paste0("ORF verse SES linear model for grade ",uniqueFeat[j]," treat phase ",k),col='red')
    # fit15.rq <- rq(Y~X,tau=.15)
    # fit85.rq <- rq(Y~X,tau=.85)
    # abline(fit15.rq$coefficients[1],fit15.rq$coefficients[2],col=unlist(colormap[as.character(k)]))
    # abline(fit85.rq$coefficients[1],fit85.rq$coefficients[2],col=unlist(colormap[as.character(k)]))
    }
    SES$sesindex =SESind
    SES %>%
        group_by(as.factor(SES$treat_phase)) %>%
        do(cor = cor(.$orf,.$sesindex)) %>%
        unnest()
  }
}
```

# Quantile Regression differences from Baseline to endline

```{r quantileDiffs,echo=FALSE, warning=FALSE}
subpopFeats = c("grade")
for (i in 1:length(subpopFeats)){
  uniqueFeat = unique(unlist(data[,subpopFeats[i]]))
  for (j in 1:length(uniqueFeat)){
    subpopMask <- dataTemporal[,subpopFeats[i]] == uniqueFeat[j] 
    SES <- na.omit(dataTemporal[subpopMask,c("orf.base","orf.end",paste0(SESfeat,".base"))])
    colnames(SES) <- c("orf.base","orf.end",SESfeat)
    SESindbl <-  projPC(SES[,SESfeat])
    temp <- na.omit(dataTemporal[subpopMask,c("orf.base","orf.end",paste0(SESfeat,".end"))])
    colnames(temp) <- c("orf.base","orf.end",SESfeat)
    SESindel <-  projPC(SES[,SESfeat])
    
    plotrange <- data.frame(X= seq(min(SESind),max(SESind),length=250))
    
    Ybl = unlist(SES[,"orf.base"])
    Xbl = SESindbl
    
    regdatabl <- data.frame(X= Xbl,Y=Ybl)
    quadratbl <- Y~ a*X^2+b*X+c
    fit15.rqbl <- nlrq(quadratbl, data=regdatabl, start= list(a=1,b=1,c=1),tau=.15)
    fit85.rqbl <- nlrq(quadratbl, data=regdatabl, start= list(a=1,b=1,c=1),tau=.85)
    reg15bl <- within(plotrange,Y <- predict(fit15.rqbl, newdata= plotrange))
    reg85bl <- within(plotrange,Y <- predict(fit85.rqbl, newdata= plotrange))
    
    Yel = unlist(SES[,"orf.end"])
    Xel = SESindel
    
    regdatael <- data.frame(X= Xel,Y=Yel)
    quadratel <- Y~ a*X^2+b*X+c
    fit15.rqel <- nlrq(quadratel, data=regdatael, start= list(a=1,b=1,c=1),tau=.15)
    fit85.rqel <- nlrq(quadratel, data=regdatael, start= list(a=1,b=1,c=1),tau=.85)
    reg15el <- within(plotrange,Y <- predict(fit15.rqel, newdata= plotrange))
    reg85el <- within(plotrange,Y <- predict(fit85.rqel, newdata= plotrange))
    
    difference15 <- data.frame(X=reg15el$X ,Y=(reg15el$Y- reg15bl$Y))
    difference85 <- data.frame(X=reg85el$X ,Y=(reg85el$Y- reg85bl$Y))
    plot((Xbl+Xel)/2,Yel-Ybl,main=paste0("Difference of Quantile Regressions, grade",uniqueFeat[j] ))
    lines(Y~X, data =difference15,add=TRUE, col ="red")
    lines(Y~X, data =difference85, add=TRUE,col = "blue")
    
    
  }
}
```

# SES index verse Population-normalized ORF

An alternative manner of considering oral reading fluency as it is affected by factors of grade and social economic status is to adjust oral reading frequency within each grade by normalizing and attempting to explain this normalized correlation using with SES data. 

```{r subpopAdjusted, echo=FALSE}
SES <- na.omit(data[,c(features,SESfeat)])
plcolors <- alpha(unlist(lapply(SES$treat_phase,function(x) colormap[as.character(x)])),.4)
grades = unique(unlist(SES$grade))
for (i in 1:length(grades)){
  phases = unique(unlist(data[data$grade==grades[i],"treat_phase"]))
  for (j in 1:length(phases)){
    mask <- SES$grade==grades[i]& SES$treat_phase==phases[j]
    subpopSES <- na.omit(SES[mask,"orf"])
    spMean <- mean(subpopSES$orf)
    spVar <- var(subpopSES$orf)
    SES[mask,"orf"] <- (SES[mask,"orf"] - spMean)/spVar
  }
}

SESind <-  projPC(SES[,SESfeat])
plot(SESind,SES$orf,col=plcolors, main= "Population-normalized ORF verse SES index")
legend("topleft", legend=colnames(colormap), pch=16,col=unlist(colormap))
# plot(SESind,SES$orf,col=as.factor(SES$treat_phase),main = "Population-normalized ORF verse SES index")
# legend("topleft", legend=levels(as.factor(SES$treat_phase)), pch=16,col=unique(as.factor(SES$treat_phase)))
# abline(1,0)
for( k in unique(as.factor(SES$treat_phase))){
    Y = unlist(SES[as.character(SES$treat_phase)==k,"orf"])
    X = SESind[as.character(SES$treat_phase)==k]
    # plot(X,Y,main = paste0("Population-normalized ORF verse SES index, treat phase ",k),col='red')
    regdata <- data.frame(X= X,Y=Y)
    quadrat <- Y~ a*X^2+b*X+c
    fit15.rq <- nlrq(quadrat, data=regdata, start= list(a=1,b=1,c=1),tau=.15)
    fit85.rq <- nlrq(quadrat, data=regdata, start= list(a=1,b=1,c=1),tau=.85)
    plotrange <- data.frame(X= seq(min(SESind),max(SESind),length=250))
    reg15 <- within(plotrange,Y <- predict(fit15.rq, newdata= plotrange))
    lines(Y~X, data =reg15, col= unlist(colormap[as.character(k)]), add=TRUE)
    reg85 <- within(plotrange,Y <- predict(fit85.rq, newdata= plotrange))
    lines(Y~X, data =reg85, col= unlist(colormap[as.character(k)]), add=TRUE)
    print(paste0("Treat phase ",k," quantile regression tests:"))
    print(summary(fit15.rq))
    print(summary(fit85.rq))
    # fit15.rq <- rq(Y~X,tau=.15)
    # fit85.rq <- rq(Y~X,tau=.85)
    # abline(fit15.rq$coefficients[1],fit15.rq$coefficients[2],col=unlist(colormap[as.character(k)]))
    # abline(fit85.rq$coefficients[1],fit85.rq$coefficients[2],col=unlist(colormap[as.character(k)]))
    }
# fit15.rq <- rq(SES$orf~SESind,tau=.15)
# fit85.rq <- rq(SES$orf~SESind,tau=.85)
# abline(fit15.rq$coefficients[1],fit15.rq$coefficients[2],col="red")
# abline(fit85.rq$coefficients[1],fit85.rq$coefficients[2],col="red")

adjmodel <- lm(orf~.-grade-orf-treat_phase,data=SES)
SESlm <- predict(adjmodel, newdata = SES)
plot(SESlm,SES$orf,col=plcolors, main= "Population-normalized ORF verse linear model index")
legend("topleft", legend=colnames(colormap), pch=16,col=unlist(colormap))
# plot(SESlm, SES$orf,col=as.factor(SES$treat_phase),main = "Population-normalized ORF verse linear model index")
# legend("topleft", legend=levels(as.factor(SES$treat_phase)), pch=16,col=unique(as.factor(SES$treat_phase)))
# abline(1,0)
for( k in unique(as.factor(SES$treat_phase))){
    Y = unlist(SES[as.character(SES$treat_phase)==k,"orf"])
    X = SESlm[as.character(SES$treat_phase)==k]
    # plot(X,Y,main = paste0("Population-normalized ORF verse linear model index, treat phase ",k),col='red')
    regdata <- data.frame(X= X,Y=Y)
    quadrat <- Y~ a*X^2+b*X+c
    fit15.rq <- nlrq(quadrat, data=regdata, start= list(a=1,b=1,c=1),tau=.15)
    fit85.rq <- nlrq(quadrat, data=regdata, start= list(a=1,b=1,c=1),tau=.85)
    plotrange <- data.frame(X= seq(min(SESlm),max(SESlm),length=250))
    reg15 <- within(plotrange,Y <- predict(fit15.rq, newdata= plotrange))
    lines(Y~X, data =reg15, col= unlist(colormap[as.character(k)]), add=TRUE)
    reg85 <- within(plotrange,Y <- predict(fit85.rq, newdata= plotrange))
    lines(Y~X, data =reg85, col= unlist(colormap[as.character(k)]), add=TRUE)
    print(paste0("Treat phase ",k," quantile regression tests:"))
    print(summary(fit15.rq))
    print(summary(fit85.rq))
    # fit15.rq <- rq(Y~X,tau=.15)
    # fit85.rq <- rq(Y~X,tau=.85)
    # abline(fit15.rq$coefficients[1],fit15.rq$coefficients[2],col=unlist(colormap[as.character(k)]))
    # abline(fit85.rq$coefficients[1],fit85.rq$coefficients[2],col=unlist(colormap[as.character(k)]))
    }
# fit15.rq <- rq(SES$orf~SESlm,tau=.15)
# fit85.rq <- rq(SES$orf~SESlm,tau=.85)
# abline(fit15.rq$coefficients[1],fit15.rq$coefficients[2],col="red")
# abline(fit85.rq$coefficients[1],fit85.rq$coefficients[2],col="red")
```

# SES index verse change in ORF

We are interested how out SES index relates to the change in Oral Reading Frequency for students with both baseline and endline data.

```{r treatPhase,echo=FALSE}
subpopFeats = c("grade")
for (i in 1:length(subpopFeats)){
  uniqueFeat = unique(unlist(dataTemporal[,subpopFeats[i]]))
  for (j in 1:length(uniqueFeat)){
    subpopMask <- dataTemporal[,subpopFeats[i]] == uniqueFeat[j] 
    SES <- na.omit(dataTemporal[subpopMask,])
    temp <- SES[,paste0(SESfeat,".base")]
    colnames(temp) <- SESfeat
    SESind <- projPC(temp)
    plot(SESind,SES$orf.end-SES$orf.base, main=paste0("Change in ORF verse SES index for grade ",uniqueFeat[j] ))
    fit15.rq <- rq((SES$orf.end-SES$orf.base)~SESind,tau=.15)
    fit85.rq <- rq((SES$orf.end-SES$orf.base)~SESind,tau=.85)
    abline(fit15.rq$coefficients[1],fit15.rq$coefficients[2],col="red")
    abline(fit85.rq$coefficients[1],fit85.rq$coefficients[2],col="red")
    hist(SES$orf.end-SES$orf.base,20,main=paste0("Change in ORF for grade ",uniqueFeat[j] ))
    
    print(paste0("Correlation of SES index and change in ORF for grade ", uniqueFeat[j],": ",cor(SESind,SES$orf.end-SES$orf.base)))
    print(paste0("Correlation of SES index and baseline ORF for grade ", uniqueFeat[j],": ",cor(SESind,SES$orf.base)))
    print(paste0("Correlation of SES index and endline ORF for grade ", uniqueFeat[j],": ",cor(SESind,SES$orf.end)))
  }
}
```

# N-tile SES-index Analysis of Gini and Mean ORF
First we conduct quantile analysis, evaluating the Gini coefficient and mean ORF for each of the 2,3,4-tiles of our SES index. 
```{r tertile,echo=FALSE, eval=FALSE, include=FALSE}
temp <- dataTemporal[,paste0(SESfeat,".base")]
colnames(temp) <- SESfeat
SESind <-  projPC(temp)
T1 <- SESind<quantile(SESind, 1/3)
T2 <- (SESind<quantile(SESind, 2/3)) & !T1
T3 <- !T1 & !T2
giniTertile <- data.frame(matrix(ncol=3,nrow=3))
colnames(giniTertile) <- c("Baseline", "Endline","Change")
rownames(giniTertile) <- c("1st Tertile","2nd Tertile","3rd Tertile")
MRFTertile <- data.frame(matrix(ncol=3,nrow=3))
colnames(MRFTertile) <- c("Baseline", "Endline","Change")
rownames(MRFTertile) <- c("1st Tertile","2nd Tertile","3rd Tertile")
for(i in 1:3){
  bl <- na.omit(dataTemporal[get(paste0("T",i)),"orf.base"])
  el <- na.omit(dataTemporal[get(paste0("T",i)),"orf.end"])
  giniTertile[i,"Baseline"] <- Gini(bl)
  giniTertile[i,"Endline"] <- Gini(el)
  giniTertile[i,"Change"] <- giniTertile[i,"Endline"] - giniTertile[i,"Baseline"]
  MRFTertile[i,"Baseline"] <- mean(bl)
  MRFTertile[i,"Endline"] <- mean(el)
  MRFTertile[i,"Change"] <- MRFTertile[i,"Endline"] - MRFTertile[i,"Baseline"]
}
print("Gini Coefficient")
print(giniTertile)

print("Mean Reading Fluency")
print(MRFTertile)
```
A T-test demonstrates that there is a statistically significant difference in the change in MRF for the lowest and highest tertile of our SES index.
```{r ttest, eval=FALSE, include=FALSE}
t.test(dataTemporal[T1,"orf.end"]-dataTemporal[T1,"orf.base"],(dataTemporal[T3,"orf.end"]-dataTemporal[T3,"orf.base"]))
```
Secondly we conduct the same analysis by medians
```{r median, echo=FALSE, eval=FALSE, include=FALSE}
M1 <- SESind<quantile(SESind, 1/2)
M2 <- !M1
giniMed <- data.frame(matrix(ncol=3,nrow=2))
colnames(giniMed) <- c("Baseline", "Endline","Change")
rownames(giniMed) <- c("1st Median","2nd Median")
MRFMed <- data.frame(matrix(ncol=3,nrow=2))
colnames(MRFMed) <- c("Baseline", "Endline","Change")
rownames(MRFMed) <- c("1st Median","2nd Median")
for(i in 1:2){
  bl <- na.omit(dataTemporal[get(paste0("M",i)),"orf.base"])
  el <- na.omit(dataTemporal[get(paste0("M",i)),"orf.end"])
  giniMed[i,"Baseline"] <- Gini(bl)
  giniMed[i,"Endline"] <- Gini(el)
  giniMed[i,"Change"] <-  giniMed[i,"Endline"] - giniMed[i,"Baseline"]
  MRFMed[i,"Baseline"] <- mean(bl)
  MRFMed[i,"Endline"] <- mean(el)
  MRFMed[i,"Change"] <- MRFTertile[i,"Endline"] - MRFTertile[i,"Baseline"]
}
print("Gini Coefficient")
print(giniMed)

print("Mean Reading Fluency")
print(MRFMed)
```
It appears from the above analysis that the majority of change in MRF occurs in the lowest tertile of wealth. 

```{r ntiles,echo=FALSE}
ntiles = c(2,3,4)
temp <- dataTemporal[,paste0(SESfeat,".base")]
colnames(temp) <- SESfeat
SESind <-  projPC(temp)
subpopVars <- c("language","grade")
{
  subpopVars <- subpopVars[unlist(lapply(subpopVars, function(x) length(unlist(unique(data[,x])))))>1]
  subpops <- unique(apply(data[,subpopVars],1,function(x) paste0(sort(x),collapse="-")))
  subpoplabels <- unique(apply(data[,subpopVars],1,function(x) paste0(subpopVars,": ",sort(x),collapse=", ")))
  nsubpops <- length(subpops)
  subpopmasks <- matrix(ncol=nsubpops,nrow=length(SESind))
  for(sp in 1:nsubpops){
    masktemp <- rep(TRUE, length(SESind))
    indstart = 1
    for(spv in 1:length(subpopVars)){
      if(spv < length(subpopVars)){
      indend = gregexpr("-",subpops[spv])[[1]][spv]-1
      }else{
      indend = nchar(subpops[sp])
      }
      masktemp <- masktemp & (as.character(unlist(dataTemporal[,subpopVars[spv]]))==substr(subpops[sp],indstart,indend))
      indstart = indend+2
    }
    subpopmasks[,sp] <- masktemp
  }
  nonemptysubpop <- colSums(subpopmasks)>0
  subpoplabels <- subpoplabels[nonemptysubpop]
  subpops <- subpops[nonemptysubpop]
  subpopmasks <- subpopmasks[,nonemptysubpop]
  nsubpops <- length(subpops)
}
for(ns in 1:length(ntiles)){
ntile = ntiles[ns]

ntilemasks <- matrix(ncol=ntile,nrow=length(SESind))
for(p in 1:(ntile)){
  ntilemasks[,p] <- (SESind<quantile(SESind, (p)/(ntile))) & (SESind>=quantile(SESind, (p-1)/ntile))
}
ntileTab <- data.frame(matrix(ncol=(2*nsubpops+2),nrow=(4*(ntile+1)+3)))
ntileTab[(0:3)*(ntile+1)+3,1] <- c("Gini","CV","%0","MRF")
ntileTab[3+4*(ntile+1),1] <- "Count"
ntileTab[3:(4*(ntile+1)+2),2] <- rep(c(1:ntile,"All"), 4)
ntileTab[1,(1:nsubpops)*2+1] <- c(subpoplabels)
ntileTab[2,0:(2*nsubpops)+2] <- c("Q#",rep(c("Baseline","Endline"),2))
for(sp in 1:nsubpops){
  bl <- na.omit(dataTemporal[subpopmasks[,sp],"orf.base"])
  el <- na.omit(dataTemporal[subpopmasks[,sp],"orf.end"])
  ntileTab[2+(ntile+1),2+2*(sp-1)+1] <- Gini(bl) #BL gini Qi
  ntileTab[2+(ntile+1),2+2*(sp-1)+2] <- Gini(el) #EL gini Qi
    
  ntileTab[2+2*(ntile+1),2+2*(sp-1)+1] <- sd(bl)/mean(bl) #BL CV Qi
  ntileTab[2+2*(ntile+1),2+2*(sp-1)+2] <- sd(el)/mean(el) #EL CV Qi
    
  ntileTab[2+3*(ntile+1),2+2*(sp-1)+1] <- sum(bl==0)/length(bl)#BL %0 Qi
  ntileTab[2+3*(ntile+1),2+2*(sp-1)+2] <- sum(el==0)/length(el)#EL %0 Qi
    
  ntileTab[2+4*(ntile+1),2+2*(sp-1)+1] <- mean(bl) #BL MRF Qi
  ntileTab[2+4*(ntile+1),2+2*(sp-1)+2] <- mean(el) #EL MRF Qi
  
  ntileTab[3+4*(ntile+1),2+2*(sp-1)+1] <- length(bl) 
  ntileTab[3+4*(ntile+1),2+2*(sp-1)+2] <- length(el) 

for(i in 1:ntile){
  ntileSubpopMask <- ntilemasks[,i] & subpopmasks[,sp]
  bl <- na.omit(dataTemporal[ntileSubpopMask,"orf.base"])
  el <- na.omit(dataTemporal[ntileSubpopMask,"orf.end"])
  ntileTab[2+i,2+2*(sp-1)+1] <- Gini(bl) #BL gini Qi
  ntileTab[2+i,2+2*(sp-1)+2] <- Gini(el) #EL gini Qi
    
  ntileTab[2+(ntile+1)+i,2+2*(sp-1)+1] <- sd(bl)/mean(bl) #BL CV Qi
  ntileTab[2+(ntile+1)+i,2+2*(sp-1)+2] <- sd(el)/mean(el) #EL CV Qi
    
  ntileTab[2+2*(ntile+1)+i,2+2*(sp-1)+1] <- sum(bl==0)/length(bl)#BL %0 Qi
  ntileTab[2+2*(ntile+1)+i,2+2*(sp-1)+2] <- sum(el==0)/length(el)#EL %0 Qi
    
  ntileTab[2+3*(ntile+1)+i,2+2*(sp-1)+1] <- mean(bl) #BL MRF Qi
  ntileTab[2+3*(ntile+1)+i,2+2*(sp-1)+2] <- mean(el) #EL MRF Qi
  ntileTab[3:nrow(ntileTab),2+2*(sp-1)+1] <- round(as.numeric(ntileTab[3:nrow(ntileTab),2+2*(sp-1)+1]),digits=3)
  ntileTab[3:nrow(ntileTab),2+2*(sp-1)+2] <- round(as.numeric(ntileTab[3:nrow(ntileTab),2+2*(sp-1)+2]),digits=3)
}
LowestNtileMRFchange <- dataTemporal[ntilemasks[,1] & subpopmasks[,sp],"orf.end"]-dataTemporal[ntilemasks[,1] & subpopmasks[,sp],"orf.base"]
TopNtileMRFchange <- dataTemporal[ntilemasks[,ncol(ntilemasks)] & subpopmasks[,sp],"orf.end"]-dataTemporal[ntilemasks[,ncol(ntilemasks)] & subpopmasks[,sp],"orf.base"]
print(t.test(LowestNtileMRFchange,TopNtileMRFchange))
}

ntileTab[is.na(ntileTab)] <- ""
print(ntileTab, row.names=FALSE,col.names=FALSE)
}
```

# Linear Model

```{r ntileslm,echo=FALSE}
ntiles = c(2,3,4)
temp <- dataTemporal[,c("orf.base",paste0(SESfeat,".base"))]
lmmodel <- lm(orf.base~.-orf.base,data=temp)
SESind <- predict(lmmodel, newdata = temp)
subpopVars <- c("language","grade")

{
  subpopVars <- subpopVars[unlist(lapply(subpopVars, function(x) length(unlist(unique(data[,x])))))>1]
  subpops <- unique(apply(data[,subpopVars],1,function(x) paste0(sort(x),collapse="-")))
  subpoplabels <- unique(apply(data[,subpopVars],1,function(x) paste0(subpopVars,": ",sort(x),collapse=", ")))
  nsubpops <- length(subpops)
  subpopmasks <- matrix(ncol=nsubpops,nrow=length(SESind))
  for(sp in 1:nsubpops){
    masktemp <- rep(TRUE, length(SESind))
    indstart = 1
    for(spv in 1:length(subpopVars)){
      if(spv < length(subpopVars)){
      indend = gregexpr("-",subpops[spv])[[1]][spv]-1
      }else{
      indend = nchar(subpops[sp])
      }
      masktemp <- masktemp & (as.character(unlist(dataTemporal[,subpopVars[spv]]))==substr(subpops[sp],indstart,indend))
      indstart = indend+2
    }
    subpopmasks[,sp] <- masktemp
  }
  nonemptysubpop <- colSums(subpopmasks)>0
  subpoplabels <- subpoplabels[nonemptysubpop]
  subpops <- subpops[nonemptysubpop]
  subpopmasks <- subpopmasks[,nonemptysubpop]
  nsubpops <- length(subpops)
}
for(ns in 1:length(ntiles)){
ntile = ntiles[ns]

ntilemasks <- matrix(ncol=ntile,nrow=length(SESind))
for(p in 1:(ntile)){
  ntilemasks[,p] <- (SESind<quantile(SESind, (p)/(ntile))) & (SESind>=quantile(SESind, (p-1)/ntile))
}
ntileTab <- data.frame(matrix(ncol=(2*nsubpops+2),nrow=(4*(ntile+1)+3)))
ntileTab[(0:3)*(ntile+1)+3,1] <- c("Gini","CV","%0","MRF")
ntileTab[3+4*(ntile+1),1] <- "Count"
ntileTab[3:(4*(ntile+1)+2),2] <- rep(c(1:ntile,"All"), 4)
ntileTab[1,(1:nsubpops)*2+1] <- c(subpoplabels)
ntileTab[2,0:(2*nsubpops)+2] <- c("Q#",rep(c("Baseline","Endline"),2))
for(sp in 1:nsubpops){
  bl <- na.omit(dataTemporal[subpopmasks[,sp],"orf.base"])
  el <- na.omit(dataTemporal[subpopmasks[,sp],"orf.end"])
  ntileTab[2+(ntile+1),2+2*(sp-1)+1] <- Gini(bl) #BL gini Qi
  ntileTab[2+(ntile+1),2+2*(sp-1)+2] <- Gini(el) #EL gini Qi
    
  ntileTab[2+2*(ntile+1),2+2*(sp-1)+1] <- sd(bl)/mean(bl) #BL CV Qi
  ntileTab[2+2*(ntile+1),2+2*(sp-1)+2] <- sd(el)/mean(el) #EL CV Qi
    
  ntileTab[2+3*(ntile+1),2+2*(sp-1)+1] <- sum(bl==0)/length(bl)#BL %0 Qi
  ntileTab[2+3*(ntile+1),2+2*(sp-1)+2] <- sum(el==0)/length(el)#EL %0 Qi
    
  ntileTab[2+4*(ntile+1),2+2*(sp-1)+1] <- mean(bl) #BL MRF Qi
  ntileTab[2+4*(ntile+1),2+2*(sp-1)+2] <- mean(el) #EL MRF Qi
  
  ntileTab[3+4*(ntile+1),2+2*(sp-1)+1] <- length(bl) 
  ntileTab[3+4*(ntile+1),2+2*(sp-1)+2] <- length(el) 

for(i in 1:ntile){
  ntileSubpopMask <- ntilemasks[,i] & subpopmasks[,sp]
  bl <- na.omit(dataTemporal[ntileSubpopMask,"orf.base"])
  el <- na.omit(dataTemporal[ntileSubpopMask,"orf.end"])
  ntileTab[2+i,2+2*(sp-1)+1] <- Gini(bl) #BL gini Qi
  ntileTab[2+i,2+2*(sp-1)+2] <- Gini(el) #EL gini Qi
    
  ntileTab[2+(ntile+1)+i,2+2*(sp-1)+1] <- sd(bl)/mean(bl) #BL CV Qi
  ntileTab[2+(ntile+1)+i,2+2*(sp-1)+2] <- sd(el)/mean(el) #EL CV Qi
    
  ntileTab[2+2*(ntile+1)+i,2+2*(sp-1)+1] <- sum(bl==0)/length(bl)#BL %0 Qi
  ntileTab[2+2*(ntile+1)+i,2+2*(sp-1)+2] <- sum(el==0)/length(el)#EL %0 Qi
    
  ntileTab[2+3*(ntile+1)+i,2+2*(sp-1)+1] <- mean(bl) #BL MRF Qi
  ntileTab[2+3*(ntile+1)+i,2+2*(sp-1)+2] <- mean(el) #EL MRF Qi
  ntileTab[3:nrow(ntileTab),2+2*(sp-1)+1] <- round(as.numeric(ntileTab[3:nrow(ntileTab),2+2*(sp-1)+1]),digits=3)
  ntileTab[3:nrow(ntileTab),2+2*(sp-1)+2] <- round(as.numeric(ntileTab[3:nrow(ntileTab),2+2*(sp-1)+2]),digits=3)
}
LowestNtileMRFchange <- dataTemporal[ntilemasks[,1] & subpopmasks[,sp],"orf.end"]-dataTemporal[ntilemasks[,1] & subpopmasks[,sp],"orf.base"]
TopNtileMRFchange <- dataTemporal[ntilemasks[,ncol(ntilemasks)] & subpopmasks[,sp],"orf.end"]-dataTemporal[ntilemasks[,ncol(ntilemasks)] & subpopmasks[,sp],"orf.base"]
print(t.test(LowestNtileMRFchange,TopNtileMRFchange))
}

ntileTab[is.na(ntileTab)] <- ""
print(ntileTab, row.names=FALSE,col.names=FALSE)
}
```