---
title: "Uganda SES"
author: "Cole Campton"
date: "8/3/2020"
output:
  pdf_document:
    keep_tex: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(haven)
library(DescTools)
library(tidyverse)
library("quantreg")
library(RColorBrewer)
library(caret)
library(e1071)

datapath <- "D:/Users/ccampton/Documents/unesco_equity/data/SHRPUganda/English/4. 20212-2018 Uganda SHRP C1 C2 C3 S_ENGLISH_rewt.dta"
data <- read_dta(datapath)
langsub <- c("Luganda","Lugwere")
languageLabels <- attributes(data$r_language)$labels
keeplangs <- languageLabels[langsub]
langsubmask <- unlist(data$r_language) %in% keeplangs
data <- data[langsubmask,]
# label languages
data$r_language <- lapply(data$r_language,function(x) names(languageLabels[languageLabels==x]))
features <- c("grade","treat_phase","orf","language")
SESfeat = c()
for(i in c(1:5,8:10)){SESfeat <- c(SESfeat,paste0("exit_interview5",letters[i]))}
SESlabs = c("Radio","Mobile Phone","Electricity","TV","Computer","Bike","Motor Cycle","Motor Veh")

data$orf <- data$r_orf
data$language <- data$r_language
dataSES <- na.omit(data[,c("id",SESfeat)])
datameasures <- na.omit(data[,c("id",features)])
data <- merge(datameasures, dataSES, by= c("id"))

n <- length(unique(data$treat_phase))
qual_col_pals = brewer.pal.info[brewer.pal.info$category == 'qual',]
all_colors <- c('#e6194b', '#3cb44b', '#ffe119', '#4363d8', '#f58231', '#911eb4', '#46f0f0', '#f032e6', '#bcf60c', '#fabebe', '#008080', '#e6beff', '#9a6324', '#fffac8', '#800000', '#aaffc3', '#808000', '#ffd8b1', '#000075', '#808080', '#ffffff', '#000000')
col_vector = unlist(mapply(brewer.pal,qual_col_pals$maxcolors,rownames(qual_col_pals)))
colormap <- data.frame(matrix(nrow=1,ncol=n))
rownames(colormap) <- "color"
colnames(colormap) <- as.character(unique(data$treat_phase))
#colormap[as.character(unique(data$treat_phase))]= sample(col_vector,n)
colormap[as.character(unique(data$treat_phase))] <- all_colors[1:n]
```
# Coherence and Summary Statistics

First we will describe the percentage of the population which claims ownership of each asset. 
```{r summary,echo=FALSE}
PCA <- prcomp(na.omit(data[,SESfeat]))
projPC <- function(X) predict(PCA,newdata=X)[,1]
sesslope <- lm(rowSums(na.omit(data[,SESfeat]))~projPC(na.omit(data[,SESfeat])))
if(sesslope$coefficients[2]<0){
  projPC <- function(X) -predict(PCA,newdata=X)[,1]
}
ownershipPct <- colSums(data[,SESfeat])/nrow(data)
barplot(ownershipPct,las=2,names.arg=SESlabs,main="Ownership Percent of each Item")
barplot(PCA$rotation[,1],las=2,names.arg=SESlabs,main="Item weights for First Principle Component")
barplot(PCA$sdev/sum(PCA$sdev),names.arg=1:length(SESfeat),main="Variance explained by each Principle Component")
plot(projPC(na.omit(data[,SESfeat])),rowSums(na.omit(data[,SESfeat])),ylab="#items owned",xlab="SES index",main="Items owned vs SES Index")
# 
# CC <- cor(data[,SESfeat] - colSums(data[,SESfeat])/nrow(data))
# CC <- abs(CC-1)
# evCC <- eigen(CC)
# evCC <- evCC$vectors[,1]
# evCC <- evCC*min(sign(evCC))
# projPC2 <- function(X) rowSums(mapply('*',X,evCC))
# plot(projPC2(na.omit(data[,SESfeat])),rowSums(na.omit(data[,SESfeat])),ylab="#items owned",xlab="SES index",main="Items owned vs SES Index")
```
There are no students which were observed at two of baseline, midline or endline, meaning there is no opportunity for validating consistency of answers to SES questions. 
```{r coherence}
overlap = matrix(data= 0, nrow=8,ncol=8)
for(i in 1:8){
  di <- na.omit(data[data$treat_phase==i,"id"])
  overlap[i,i] <- length(di)
  for(j in min((i+1),8):8){
    dj <- na.omit(data[data$treat_phase==j,"id"])
    overlap[i,j] <- length(unlist(intersect(di,dj)))
  }
}
print(overlap)
```


<!-- # Quantile Regression differences from Baseline to endline -->


# N-tile SES-index Analysis of Gini and Mean ORF
First we conduct quantile analysis, evaluating the Gini coefficient, mean ORF, CV, and percent zero for each of the 2,3,4-tiles of our SES index. 
We segment into subpopulations by language and grade, producing quantile regressions for 
It appears from the above analysis that the majority of change in MRF occurs in the lowest tertile of wealth. 

```{r ntiles,echo=FALSE, warning=FALSE}
mode <- function(x) names(table(unlist(x)))[table(unlist(x))==max(table(unlist(x)))]
library(IC2)
zero2na <- function(x) ifelse(x==0,NA,x)
ntiles = c(2,3,4)
normorf <- matrix(NA, ncol=1,nrow=nrow(data))

phases <- sort(unlist(unique(unlist(data[,"treat_phase"]))))
nphases <- length(phases)
SESind <-  projPC(data)
subpopVars <- c("grade","language")
#Compute Subpop labels, and masks for non-empty subpops (uses all phases)
{
  subpopVars <- subpopVars[unlist(lapply(subpopVars, function(x) length(unlist(unique(data[,x])))))>1]
  if(length(subpopVars)>1){
    subpops <- unique(apply(data[,subpopVars],1,function(x) paste0(x,collapse="-")))
    subpoplabels <- unique(apply(data[,subpopVars],1,function(x) paste0(subpopVars,": ",x,collapse=", ")))
  }else{
    subpops <-unique(data[,subpopVars])
    subpoplabels <- paste(subpopVars,subpops)
  }
  nsubpops <- length(subpops)
  subpopmasks <- matrix(ncol=nsubpops,nrow=length(SESind))
  for(sp in 1:nsubpops){
    masktemp <- rep(TRUE, length(SESind))
    indstart = 1
    for(spv in 1:length(subpopVars)){
      if(spv < length(subpopVars)){
      indend = gregexpr("-",subpops[spv])[[1]][spv]-1
      }else{
      indend = nchar(subpops[sp])
      }
      masktemp <- masktemp & (as.character(unlist(data[,subpopVars[spv]]))==substr(subpops[sp],indstart,indend))
      indstart = indend+2
    }
    subpopmasks[,sp] <- masktemp
  }
  nonemptysubpop <- colSums(subpopmasks)>0
  subpoplabels <- subpoplabels[nonemptysubpop]
  subpops <- subpops[nonemptysubpop]
  subpopmasks <- subpopmasks[,nonemptysubpop]
  nsubpops <- length(subpops)
}

xlsxCols <- c("dataset",	"performance_measure"	,"measure_label","grade", "treat_phase","ge2_for_subpop","gini","mean", "cv", "ratio_p90p10","ratio_p75p25", "pct_zero")
UgandaXlsx <- (matrix('',nrow = nphases*nsubpops+1,ncol = length(xlsxCols)))
UgandaXlsx[1,] <- xlsxCols

for(ns in 1:length(ntiles)){
ntile = ntiles[ns]
# Generate n-tile masks
{
  ntilemasks <- matrix(ncol=ntile,nrow=length(SESind))
  for(p in 1:(ntile)){
    ntilemasks[,p] <- (SESind<quantile(SESind, (p)/(ntile))) & (SESind>=quantile(SESind, (p-1)/ntile))
  }
}
# Intialize table, build labels
{
  ntileTab <- data.frame(matrix(ncol=(nphases*nsubpops+2),nrow=(4*(ntile+1)+3)))
  ntileTab[(0:3)*(ntile+1)+3,1] <- c("Gini","CV","%0","MRF")
  ntileTab[3:(4*(ntile+1)+2),2] <- rep(c(1:ntile,"All"), 4)
  ntileTab[1,(1:nsubpops)*nphases+1] <- c(subpoplabels)
  ntileTab[2,0:(nphases*nsubpops)+2] <- c("Q#",rep(phases,nsubpops))
  ntileTab[(4*(ntile+1)+3),1 ] <- "Counts"
}
for(sp in 1:nsubpops){
  SES <- na.omit(data[subpopmasks[,sp],c("orf","treat_phase","grade","language",SESfeat)])
  #ORF verse SES index by sub-populations
  if(ns==1){
    SESind <-  projPC(SES[,SESfeat])
    plcolors <- alpha(unlist(lapply(SES$treat_phase,function(x) colormap[as.character(x)])),.4)
    plot(SESind,unlist(SES$orf),col=plcolors, main= paste0("ORF verse SES index by phase, ",subpoplabels[sp] ))
    legend("topleft", legend=colnames(colormap), pch=16,col=unlist(colormap))
  }
  for( p in 1:nphases){
    phase = phases[p]
    phasemask <- as.character(SES$treat_phase)==as.character(phase)
    # #ORF verse SES index colored by treatment phase
    if(ns==1){
      if(sum(phasemask)>2){
        Y = unlist(SES[phasemask,"orf"])
        X = SESind[phasemask]
        regdata <- data.frame(X= X,Y=Y)
        quadrat <- Y~ a*X^2+b*X+c
        fit15.rq <- nlrq(quadrat, data=regdata, start= list(a=1,b=1,c=1),tau=.15)
        fit85.rq <- nlrq(quadrat, data=regdata, start= list(a=1,b=1,c=1),tau=.85)
        plotrange <- data.frame(X= seq(min(SESind),max(SESind),length=250))
        reg15 <- within(plotrange,Y <- predict(fit15.rq, newdata= plotrange))
        lines(Y~X, data =reg15, col= unlist(colormap[as.character(phase)]), add=TRUE)
        reg85 <- within(plotrange,Y <- predict(fit85.rq, newdata= plotrange))
        lines(Y~X, data =reg85, col= unlist(colormap[as.character(phase)]), add=TRUE)
        print(paste0("Treat phase ",phase," quantile regression tests:"))
        print(summary(fit15.rq))
        print(summary(fit85.rq))
      }
    }
    #Compute normalize orf for phase, subpop
    if(ns==1){
        normMask <- subpopmasks[,sp] & unlist(as.character(data$treat_phase)==as.character(phase))
        if(sum(normMask)>0){
        spMean <- mean(unlist(data[normMask,"orf"]))
        spVar <- var(unlist(data[normMask,"orf"]))
        if(is.na(spVar)){
          spVar <- 1
        }
        normorf[normMask] <- (unlist(data[normMask,"orf"]) - spMean)/spVar
        }
    }
    #Overall phase, subpop measures
    {
    SESphase <- unlist(na.omit(SES[phasemask,"orf"]))
    if(sum(phasemask)>2){
    ntileTab[2+(ntile+1),2+nphases*(sp-1)+p] <- Gini(SESphase) #gini Qi
      
    ntileTab[2+2*(ntile+1),2+nphases*(sp-1)+p] <- sd(SESphase)/mean(SESphase) #CV Qi
      
    ntileTab[2+3*(ntile+1),2+nphases*(sp-1)+p] <- sum(SESphase==0)/length(SESphase)#%0 Qi
      
    ntileTab[2+4*(ntile+1),2+nphases*(sp-1)+p] <- mean(SESphase) #MRF Qi
    ntileTab[3+4*(ntile+1),2+nphases*(sp-1)+p] <- length(SESphase)
    
    xlsxphase <- na.omit(SES[phasemask,])
    
    UgandaXlsx[(sp-1)*nphases+p+1,] <- c('Uganda','r_orf', mode(xlsxphase$language), mode(xlsxphase$grade), mode(xlsxphase$treat_phase), ifelse(mean(SESphase)==0, 0, calcGEI(SESphase, alpha=2)$ineq$index),Gini(SESphase), mean(SESphase), sd(SESphase)/mean(SESphase), quantile(SESphase,.90)/zero2na(quantile(SESphase,.10)), quantile(SESphase,.75)/zero2na(quantile(SESphase,.25)), sum(SESphase==0)/length(SESphase))
    }
    }
    # Add n-tile measures for of of the n n-tiles
    for(i in 1:ntile){
      phase = phases[p]
      ntileSubpopMask <- ntilemasks[,i] & subpopmasks[,sp] & as.character(data$treat_phase)==as.character(phase)
      if(sum(ntileSubpopMask)>0){
      SESntile <- unlist(na.omit(data[ntileSubpopMask,"orf"]))
      
      ntileTab[2+i,2+nphases*(sp-1)+p] <- Gini(SESntile) #gini Qi
        
      ntileTab[2+1*(ntile+1)+i,2+nphases*(sp-1)+p] <- sd(SESntile)/mean(SESntile) #CV Qi
        
      ntileTab[2+2*(ntile+1)+i,2+nphases*(sp-1)+p] <- sum(SESntile==0)/length(SESntile)#%0 Qi
        
      ntileTab[2+3*(ntile+1)+i,2+nphases*(sp-1)+p] <- mean(SESntile) #MRF Qi
      ntileTab[3:nrow(ntileTab),2+nphases*(sp-1)+p] <- round(as.numeric(ntileTab[3:nrow(ntileTab),2+nphases*(sp-1)+p]),digits=3)
      }
      }
  }
  #T-test for ???
  {  
# LowestNtileMRFchange <- data[ntilemasks[,1] & subpopmasks[,sp] & data$treat_phase==phases[1],"orf"]-data[ntilemasks[,1] & subpopmasks[,sp] & data$treat_phase==phases[length(phases)],"orf"]
# TopNtileMRFchange <- dataTemporal[ntilemasks[,ncol(ntilemasks)] & subpopmasks[,sp],"orf.end"]-dataTemporal[ntilemasks[,ncol(ntilemasks)] & subpopmasks[,sp],"orf.base"]
# print(t.test(LowestNtileMRFchange,TopNtileMRFchange))
  }
}

# Subpop-normalized plots
if(ns==1){
SES <- na.omit(data[,c("treat_phase",SESfeat)])
SESind <-  projPC(SES[,SESfeat])
# plot(SESind,normorf,col=plcolors, main= "Population-normalized ORF verse SES index")
plot(SESind,normorf,type='n', ylim=c(0,1.2), main= "Population-normalized ORF verse SES index")
tf <- unique(as.factor(SES$treat_phase))
for( ks in 1:length(tf)){
    k <- tf[ks]
    Y = normorf[as.character(SES$treat_phase)==k]
    Y[is.na(Y)] <- 0
    X = SESind[as.character(SES$treat_phase)==k]
    regdata <- data.frame(X= X,Y=Y)
    quadrat <- Y~ a*X^2+b*X+c
    fit15.rq <- nlrq(quadrat, data=regdata, start= list(a=1,b=1,c=1),tau=.15)
    fit85.rq <- nlrq(quadrat, data=regdata, start= list(a=1,b=1,c=1),tau=.85)
    plotrange <- data.frame(X= seq(min(SESind),max(SESind),length=250))
    reg15 <- within(plotrange,Y <- predict(fit15.rq, newdata= plotrange))
    lines(Y~X, data =reg15, col= unlist(colormap[as.character(k)]), add=TRUE)
    reg85 <- within(plotrange,Y <- predict(fit85.rq, newdata= plotrange))
    lines(Y~X, data =reg85, col= unlist(colormap[as.character(k)]), add=TRUE)
    print(paste0("Treat phase ",k," quantile regression tests:"))
    print(summary(fit15.rq))
    print(summary(fit85.rq))
}
legend("topleft", legend=colnames(colormap), pch=16,col=unlist(colormap))
cat(paste0("Standard deviation of SES: ", sd(SESind),", Standard deviation of normalized orf: ",sd(normorf),". \n"))
}

ntileTab[is.na(ntileTab)] <- ""
print(ntileTab, row.names=FALSE,col.names=FALSE)
xlsxpath = "D:/Users/ccampton/Dropbox/dukeInternInequalityOutputs/Cole/SEStables/"
write.xlsx(x = as.data.frame(ntileTab), file = paste0(xlsxpath,"SES_UgandaRlang",ntile,"-percentiles",".xlsx"),sheetName = paste0(ntile,"-percentiles"), row.names = FALSE, col.names=FALSE)


}
UgandaXlsx <- UgandaXlsx[!is.na(UgandaXlsx[,1]),]
library("xlsx")
xlsxpath = "D:/Users/ccampton/Dropbox/dukeInternInequalityOutputs/Cole/newResults/Uganda/"
write.xlsx(x = UgandaXlsx, file = paste0(xlsxpath,"inequality_results_UgandaRlang.xlsx"),sheetName = "core", row.names = FALSE, col.names=FALSE)
```

# Linear Model Tables and Plots
```{r ntilesLM,echo=FALSE, warning=FALSE}
ntiles = c(2,3,4)
normorf <- matrix(NA, ncol=1,nrow=nrow(data))

phases <- sort(unlist(unique(unlist(data[,"treat_phase"]))))
nphases <- length(phases)

temp <- unlist(data$orf)
for(i in 1:length(SESfeat)){temp <- cbind(temp,unlist(data[,SESfeat[i]]))}
rownames(temp) <- 1:nrow(temp)
colnames(temp) <- c("orf",SESfeat)
temp <- data.frame(temp)
lmmodel <- lm(orf~.-orf,data=temp)
SESind <- predict(lmmodel, newdata = temp)

subpopVars <- c("grade","language")
#Compute Subpop labels, and masks for non-empty subpops (uses all phases)
{  subpopVars <- subpopVars[unlist(lapply(subpopVars, function(x) length(unlist(unique(data[,x])))))>1]
  if(length(subpopVars)>1){
    subpops <- unique(apply(data[,subpopVars],1,function(x) paste0(x,collapse="-")))
    subpoplabels <- unique(apply(data[,subpopVars],1,function(x) paste0(subpopVars,": ",x,collapse=", ")))
  }else{
    subpops <- unique(data[,subpopVars])
    subpoplabels <- paste(subpopVars,subpops)
  }
  nsubpops <- length(subpops)
  subpopmasks <- matrix(ncol=nsubpops,nrow=length(SESind))
  for(sp in 1:nsubpops){
    masktemp <- rep(TRUE, length(SESind))
    indstart = 1
    for(spv in 1:length(subpopVars)){
      if(spv < length(subpopVars)){
      indend = gregexpr("-",subpops[spv])[[1]][spv]-1
      }else{
      indend = nchar(subpops[sp])
      }
      masktemp <- masktemp & (as.character(unlist(data[,subpopVars[spv]]))==substr(subpops[sp],indstart,indend))
      indstart = indend+2
    }
    subpopmasks[,sp] <- masktemp
  }
  nonemptysubpop <- colSums(subpopmasks)>0
  subpoplabels <- subpoplabels[nonemptysubpop]
  subpops <- subpops[nonemptysubpop]
  subpopmasks <- subpopmasks[,nonemptysubpop]
  nsubpops <- length(subpops)
}

for(ns in 1:length(ntiles)){
ntile = ntiles[ns]
# Generate n-tile masks
{
  ntilemasks <- matrix(ncol=ntile,nrow=length(SESind))
  for(p in 1:(ntile)){
    ntilemasks[,p] <- (SESind<quantile(SESind, (p)/(ntile))) & (SESind>=quantile(SESind, (p-1)/ntile))
  }
}
# Intialize table, build labels
{
  ntileTab <- data.frame(matrix(ncol=(nphases*nsubpops+2),nrow=(4*(ntile+1)+3)))
  ntileTab[(0:3)*(ntile+1)+3,1] <- c("Gini","CV","%0","MRF")
  ntileTab[3:(4*(ntile+1)+2),2] <- rep(c(1:ntile,"All"), 4)
  ntileTab[1,(1:nsubpops)*nphases+1] <- c(subpoplabels)
  ntileTab[2,0:(nphases*nsubpops)+2] <- c("Q#",rep(phases,nsubpops))
  ntileTab[(4*(ntile+1)+3),1 ] <- "Counts"
}
for(sp in 1:nsubpops){
  SES <- na.omit(data[subpopmasks[,sp],c("orf","treat_phase",SESfeat)])
  #ORF verse SES index by sub-populations
  if(ns==1){
    SESindsub <-  SESind[subpopmasks[,sp]]
    plcolors <- alpha(unlist(lapply(SES$treat_phase,function(x) colormap[as.character(x)])),.4)
    plot(SESindsub,unlist(SES$orf),col=plcolors, main= paste0("ORF verse SES index by phase, ",subpoplabels[sp] ))
    legend("topleft", legend=colnames(colormap), pch=16,col=unlist(colormap))
  }
  for( p in 1:nphases){
    phase = phases[p]
    phasemask <- as.character(SES$treat_phase)==as.character(phase)
    # #ORF verse SES index colored by treatment phase
    if(ns==1){
      if(sum(phasemask)>2){
        Y = unlist(SES[phasemask,"orf"])
        X = SESindsub[phasemask]
        regdata <- data.frame(X= X,Y=Y)
        quadrat <- Y~ a*X^2+b*X+c
        fit15.rq <- nlrq(quadrat, data=regdata, start= list(a=1,b=1,c=1),tau=.15)
        fit85.rq <- nlrq(quadrat, data=regdata, start= list(a=1,b=1,c=1),tau=.85)
        plotrange <- data.frame(X= seq(min(SESind),max(SESind),length=250))
        reg15 <- within(plotrange,Y <- predict(fit15.rq, newdata= plotrange))
        lines(Y~X, data =reg15, col= unlist(colormap[as.character(phase)]), add=TRUE)
        reg85 <- within(plotrange,Y <- predict(fit85.rq, newdata= plotrange))
        lines(Y~X, data =reg85, col= unlist(colormap[as.character(phase)]), add=TRUE)
        print(paste0("Treat phase ",phase," quantile regression tests:"))
        print(summary(fit15.rq))
        print(summary(fit85.rq))
      }
    }
    #Compute normalize orf for phase, subpop
    if(ns==1){
        normMask <- subpopmasks[,sp] & unlist(as.character(data$treat_phase)==as.character(phase))
        if(sum(normMask)>0){
        spMean <- mean(unlist(SES[phasemask,"orf"]))
        spVar <- var(unlist(SES[phasemask,"orf"]))
        if(is.na(spVar)){
          spVar <- 1
        }
        normorf[normMask] <- (unlist(data[normMask,"orf"]) - spMean)/spVar
        }
    }
    #Overall phase, subpop measures
    {
    SESphase <- unlist(na.omit(SES[phasemask,"orf"]))
    if(sum(phasemask)>2){
    ntileTab[2+(ntile+1),2+nphases*(sp-1)+p] <- Gini(SESphase) #gini Qi
      
    ntileTab[2+2*(ntile+1),2+nphases*(sp-1)+p] <- sd(SESphase)/mean(SESphase) #CV Qi
      
    ntileTab[2+3*(ntile+1),2+nphases*(sp-1)+p] <- sum(SESphase==0)/length(SESphase)#%0 Qi
      
    ntileTab[2+4*(ntile+1),2+nphases*(sp-1)+p] <- mean(SESphase) #MRF Qi
    
    ntileTab[3+4*(ntile+1),2+nphases*(sp-1)+p] <- length(SESphase)
    }
    }
    # Add n-tile measures for of of the n n-tiles
    for(i in 1:ntile){
      phase = phases[p]
      ntileSubpopMask <- ntilemasks[,i] & subpopmasks[,sp] & as.character(data$treat_phase)==as.character(phase)
      if(sum(ntileSubpopMask)>0){
      SESntile <- unlist(na.omit(data[ntileSubpopMask,"orf"]))
      
      ntileTab[2+i,2+nphases*(sp-1)+p] <- Gini(SESntile) #gini Qi
        
      ntileTab[2+1*(ntile+1)+i,2+nphases*(sp-1)+p] <- sd(SESntile)/mean(SESntile) #CV Qi
        
      ntileTab[2+2*(ntile+1)+i,2+nphases*(sp-1)+p] <- sum(SESntile==0)/length(SESntile)#%0 Qi
        
      ntileTab[2+3*(ntile+1)+i,2+nphases*(sp-1)+p] <- mean(SESntile) #MRF Qi
      ntileTab[3:nrow(ntileTab),2+nphases*(sp-1)+p] <- round(as.numeric(ntileTab[3:nrow(ntileTab),2+nphases*(sp-1)+p]),digits=3)
      }
      }
  }
}

# Subpop-normalized plots
if(ns==1){
SES <- na.omit(data[,c("treat_phase",SESfeat)])
plot(SESind,normorf,col=plcolors, main= "Population-normalized ORF verse SES index")
legend("topleft", legend=colnames(colormap), pch=16,col=unlist(colormap))
for( k in unique(as.factor(SES$treat_phase))){
    Y = normorf[as.character(SES$treat_phase)==k]
    Y[is.na(Y)] <- 0
    X = SESind[as.character(SES$treat_phase)==k]
    regdata <- data.frame(X= X,Y=Y)
    quadrat <- Y~ a*X^2+b*X+c
    fit15.rq <- nlrq(quadrat, data=regdata, start= list(a=1,b=1,c=1),tau=.15)
    fit85.rq <- nlrq(quadrat, data=regdata, start= list(a=1,b=1,c=1),tau=.85)
    plotrange <- data.frame(X= seq(min(SESind),max(SESind),length=250))
    reg15 <- within(plotrange,Y <- predict(fit15.rq, newdata= plotrange))
    lines(Y~X, data =reg15, col= unlist(colormap[as.character(k)]), add=TRUE)
    reg85 <- within(plotrange,Y <- predict(fit85.rq, newdata= plotrange))
    lines(Y~X, data =reg85, col= unlist(colormap[as.character(k)]), add=TRUE)
    print(paste0("Treat phase ",k," quantile regression tests:"))
    print(summary(fit15.rq))
    print(summary(fit85.rq))
  }
}

ntileTab[is.na(ntileTab)] <- ""
print(ntileTab, row.names=FALSE,col.names=FALSE)

}

```
